\documentclass[12pt]{article}
\usepackage{graphicx, amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{kotex}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage{tikz-cd}
\usepackage{physics}
\usepackage{enumitem}
\usepackage{mathtools}


\textwidth 6.5 truein 
\oddsidemargin 0 truein 
\evensidemargin -0.50 truein 
\topmargin -.5 truein 
\textheight 8.5in
\setlist[enumerate]{align=left}

\DeclareMathOperator{\cc}{\mathbb{C}}
\DeclareMathOperator{\zz}{\mathbb{Z}}
\DeclareMathOperator{\rr}{\mathbb{R}}
\DeclareMathOperator{\bA}{\mathbb{A}}
\DeclareMathOperator{\fra}{\mathfrak{a}}
\DeclareMathOperator{\frb}{\mathfrak{b}}
\DeclareMathOperator{\frm}{\mathfrak{m}}
\DeclareMathOperator{\frp}{\mathfrak{p}}
\DeclareMathOperator{\slin}{\mathfrak{sl}}
\DeclareMathOperator{\Lie}{\mathsf{Lie}}
\DeclareMathOperator{\Alg}{\mathsf{Alg}}
\DeclareMathOperator{\Spec}{\mathrm{Spec}}
\DeclareMathOperator{\End}{\mathrm{End}}
\DeclareMathOperator{\rad}{\mathrm{rad}}
\newcommand{\Ass}{\text{Ass}_R}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Sch}{\mathbf{Sch}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\Z}{\mathcal{Z}}
\newcommand{\tensorp}{\bigotimes}
\newcommand{\isomorp}{\cong}
\newcommand{\Ring}{\mathbf{Ring}}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}


\begin{document}


%%\title{Financial Management HW - 1} 
%%\author{SungBin Park, 20150462}
%%\maketitle
\section*{Dummit\&Foote Abstract Algebra section 15.1 Solutions for Selected Problems by 3 mod(8)}
Author: SungBin Park, Physics, 20150462
\begin{enumerate}
\item[3.] I'll a lemma to use.
\begin{lemma}
For a field $k$, $k[x]$ has infinitely many primes, which is irreducible.
\end{lemma}
\begin{proof}
Since $k$ is a field, $k{x}$ is a P.I.D, so any prime ideals are maximal ideal, and a prime element is a irreducible element. Let there are finitely many prime element: $p_1(x),p_2(x)\ldots, p_n(x)$ for $n\in \mathbb{N}$, and let $p(x)=\prod_{i=1}^n p_i(x)+1$. Since $p(x)$ is not a prime element, the $(p(x))$ should be contained in one of the maximal ideal $(p_i(x))$ for some $i$. WLOG, let $i=1$. However, $(p(x),p_1(x))=1$, so it is contradiction to $p(x)\in (p_i(x))$. Therefore, there are infinitely many primes in $k[x]$. Since primes are irreducibles in P.I.D, the last statement follows.
\end{proof}
Let $k(x)$ is finitely generated k-algebra, so $k(x)=f\left[\frac{a_1(x)}{b_1(x)},\frac{a_2(x)}{b_2(x)},\ldots, \frac{a_n(x)}{b_n(x)}\right]$ for some $n\in \mathbb{N}$, $a_i(x),b_i(x)\in k[x]$, $a(x)$ and $b(x)$ relatively prime. Since $k[x]$ is U.F.D, let $p_{ij}(x)$ be irreducible factors of $a_i(x)$, i.e., $a_i(x)=u_i\prod_{j=1}^{m_i}p_{ij}(x)$ for some unit $u_i$. By the lemma above, there is a irreducible $p(x)$ such that $p(x)\notin (p_{11}(x), \ldots, p_{1m_i}(x),p_{21}(x),\ldots, p_{nm_n}(x))$.

Let $\frac{1}{p(x)}\in k(x)=\left(\frac{a_1(x)}{b_1(x)},\frac{a_2(x)}{b_2(x)},\ldots, \frac{a_n(x)}{b_n(x)}\right)$, then $\frac{1}{p(x)}\in k\left[\frac{a_1(x)}{b_1(x)},\frac{a_2(x)}{b_2(x)},\ldots, \frac{a_n(x)}{b_n(x)}\right]$. Since $\frac{1}{p(x)}$ is not constant, and right hand side is polynomial, it would be written as $\frac{r(x)}{b_1^{n_1}\cdots b_s^{n_s}}$ for some $r(x)\in k[x]$, $n_1, \ldots,n_s, s\in \mathbb{N}\cup \{0\}$. To satisfy $\frac{1}{p(x)}=\frac{r(x)}{b_1^{n_1}\cdots b_s^{n_s}}$, $b_1^{n_1}\cdots b_s^{n_s}=p(x)r(x)$ but it means $b_1^{n_1}\cdots b_s^{n_s}$ have a irreducible factor $p(x)$ since $k[x]$ is a P.I.D which is contradiction to assumption. Therefore, $k(x)$ is not finitely generated k-algebra.

\item[11.]\begin{enumerate}
\item[(a)] Let $S$ be the set of not finitely generated ideals of $R$. I'll use Zorn's lemma to show $S$ has a maximal element in $S$: $I$.

Let $C$ be a chain in $S$, i.e. a totally ordered set in $S$ order given by set inclusion. Let $J=\cup_{A\in C} A$, then $J$ is an ideal.(The proof of thi s statement is contained in the proof of proposition 11 of section 7.4, Dummit \& Foote Abstract Algebra 3rd.) I need to show that $J\in S$. Let $J$ is finitely generated, then $J=(a_1, \ldots, a_n)$, $a_i\in J$. By the construction of $J$, $a_i$ is in some element in $C$; let a ideal $A_i$. Since $C$ is totally ordered, there exists $A=A_k$ for some $k\leq n$ such that $A_i\subset A_k$ for all $i\leq n$. Therefore, $J\subset A$ and $J=A$; therefore, $J$ is not finitely generated which is contradiction. Hence, $J\in C$.

By the Zorn's lemma, there exists a maximal element in $S$: let it $I$.
\item[(b)] Since $I$ is not a prime ideal, there exists $a,b\notin I$ such that $ab\in I$. Let $J_1=(I,a)$, $J_2=(I,b)$. Then, $I\subset J_1,J_2$ and $J_1J_2=(I^2, aI, Ib, ab)\subset I$ since $I^2\subset I$, $ab\in I$. Since $J_1,J_2\supset I$, $J_1$ and $J_2$ are finitely generated by the maximality of $I$. Let $J_1=(a_1, \ldots, a_n)$, $J_2=(b_1, \ldots, b_m)$, then $J_1J_2=(a_1b_1, a_1,b_2, \ldots, a_1b_m,a_2b_1, \ldots, a_nb_m)$. Therefore, $J_1J_2$ is finitely generated.
\item[(c)] $R/I$ is a Noetherian ring, I can show that $I/J_1J_2$ is finitely generated by proving $J_1/J_1J_2$ is finitely generated $R/I$ module according to problem 8. Since $J_1=(a_1, \ldots, a_n)$, we can represent $J_1/J_1J_2=(\overline{a_1}, \ldots, \overline{a_n})$ where $\overline{a_i}=a_i+J_1J_2$. Let's represent $m\in J_1/J_1J_2$ by $m+J_1J_2=\sum\limits_{i=1}^n (r_i+I)(a_i+J_1J_2)$ for some $r_i\in R$. If we multiply $(r+I)$, $r\in R$ to this module, 
\begin{equation*}
\begin{split}
(r+I)\left(\sum\limits_{i=1}^n \overline{r_ia_i}\right)&=\sum\limits_{i=1}^n (r+I)(r_ia_i+J_1J_2) \\
&=\sum\limits_{i=1}^n r r_ia_i+rJ_1J_2+Ir_ia+IJ_1J_2 \\
&=\sum\limits_{i=1}^n r r_ia_i+J_1J_2 \in J_1/J_2J_2.
\end{split}
\end{equation*}
It means $J_1/J_1J_2$ is finitely generated $R/I$ module and hence Noetherian.(Checking $R/I$ module properties can be made from above computation.) It implies $I/J_1J_2$, which is submodule of $J_1/J_1J_2$, is finitely generated.
\item[(d)] Since $I/J_1J_2$ is finitely generated $R/I$ module, let $I/J_1J_2=(\overline{i_1}, \ldots, \overline{i_l})$ where $i_i\in I$, $\overline{i_i}=i_1+J_1J_2$. I'll claim that $I=(i_1, \ldots, i_l, a_1b_1, \ldots, a_nb_m)$ as an ideal of $R$. It is trivial that  $I\supset(i_1, \ldots, i_l, a_1b_1, \ldots, a_nb_m)$ so I'll show the converse. Let $i\in I$, then $i+J_1J_2=\sum\limits_{j=1}^l (r_j+I)(i_j+J_1J_2)$ for some $r_j\in R$. Then, $\sum\limits_{j=1}^l (r_j+I)(i_j+J_1J_2)=\sum\limits_{j=1}^l r_ji_j+r_jJ_1J_2+Ii_j+IJ_1J_2=\sum\limits_{j=1}^l r_ji_j+J_1J_2$ since $Ii_j\in \subset I^2\subset J_1J_2$. Therefore, $i=\sum\limits_{j=1}^l r_j i_j-\sum\limits_{n,m} r_{ks}a_kb_s$. Hence $I=(i_1, \ldots, i_l, a_1b_1, \ldots, a_nb_m)$ and $I$ is finitely generated, which is contradiction to (a).
\end{enumerate}
\item[19.] Before starting, I'll state short lemmas which will be used in the proof.
\begin{lemma}
If $p(x)$ is a irreducible polynomial in $k[x]$, $\I(\Z(p(x)))=p(x)$ or $\I(\Z(p(x)))=k[x]$.
\end{lemma}
\begin{proof}
$p(x)$ is irreducible element in P.I.D, so $(p(x))$ is a maximal ideal in $k[x]$. Since $p(x)\subset \I(\Z(p(x)))$ in $k[x]$, $\I(\Z(p(x)))=(p(x))$ or $\I(\Z(p(x)))=k[x]$.
\end{proof}
\begin{lemma}
Let $\{p_1(x), p_2(x),\ldots,p_n(x)\}$ are distinct irreducible polynomials in $k[x]$, then $\bigcap_{i=1}^n (p_i(x))=\left(\prod_{i=1}^n p_i(x)\right)$.
\end{lemma}
\begin{proof}
I'll use induction on $k$ for $\left(\prod_{i=1}^k p_i(x)\right)$. For $k=1$, the lemma is trivial. For $k=s$, let $\bigcap_{i=1}^s (p_i(x))=\left(\prod_{i=1}^s p_i(x)\right)$ and $p_{s+1}(x)$ be a distinct irreducible polynomial from others. Since $\left(\prod_{i=1}^s p_i(x)\right)+p_{s+1}(x)\supset p_{s+1}(x)$, $\left(\prod_{i=1}^s p_i(x)\right)+p_{s+1}(x)=k[x]$ or $p_{s+1}(x)$. For $p_{s+1}(x)$ case, there exists $r(x)$ such that $\prod_{i=1}^s p_i(x)=r(x)p_{s+1}(x)$ which is contradiction to distinctness of $p_{s+1}(x)$ from others. Therefore, $\left(\prod_{i=1}^s p_i(x)\right)+p_{s+1}(x)=k[x]$ and $\bigcap_{i=1}^{s+1} (p_i(x))=\left(\prod_{i=1}^{s+1} p_i(x)\right)$ (cf. problem 34 in section 7.4 of Dummit \& Foote Abstract Algebra.)
\end{proof}
Let $f(x)=u\prod_{i=1}^n p_i(x)$ where $p_i(x)$ are irreducible polynomials in $k[x]$, then 
\begin{equation*}
\begin{split}
Z(f)&=\Z((f)) \\
&=\Z\left(\left(u\prod_{i=1}^n p_i(x)\right)\right) =\Z\left((u)\prod_{i=1}^n(p_i(x))\right) \\
&=\Z(u)\bigcup_{i=1}^n \Z((p_i(x))) =\bigcup_{i=1}^n \Z(p_i(x))
\end{split}.
\end{equation*}
Furthermore,  $\I\left(Z(f)\right)=\I\left(\bigcup_{i=1}^n \Z(p_i(x))\right)=\bigcap_{i=1}^n \I\left(\Z(p_i(x))\right)$. By the first lemma above, $\left(\Z(p_i(x))\right)=(p_i(x))$ or whole set and $\I\left(Z(f)\right)=\bigcap_{j=1}^m (p_{j}(x))$ discarding $k[x]$ term..... Since each $(p_i(x))$ are maximal ideals, $(p_i(x))\subset (p_j(x))$ or $(p_i(x))\supset (p_j(x))$ for $(p_i(x))+ (p_j(x))=k[x]$ or $i\neq j$. Arranging the terms which is in inclusion relation, we can write $\I\left(Z(f)\right)=\bigcap_{j=1}^m (p_{i_j}(x))$ and $p_{i_j}(x)$ are distinct. Using second lemma, furthermore, $\bigcap_{j=1}^m (p_{i_j}(x))=\prod_j^m(p_{i_j}(x))=(\prod_j^m p_{i_j}(x))$.

Let $f$ be the product of distinct linear factors in $k[x]$, i.e. $p_i(x)$ are distinct linear. Since $a\in \Z(x-a)$ for $a\in k$, $\I(\Z(p_i(x)))\neq k[x]$, so $(f)=(\prod_i^n p_i(x))$.

Conversely, let $(f)=(\prod_i^n p_i(x))$. From the proof above, $p_i(x)$ should be distinct, so I'll show that $p_i(x)$ are linear. Let $p(x)$ is a irreducible polynomial with degree more than $2$. To satisfy irreducibility, $p(x)$ does not have root in $k$, which means $\Z(p(x))=\phi$. It immediately means $\I(\Z(p(x)))=k[x]$ and this term is discarded as in the proof. Therefore, $(f)=(\prod_i^n p_i(x))$ means each $p_i(x)$ are linear.

\item[27.] Let $W=\Z(I)$, $W'=\Z(J)$ for some ideal $I,J\in k[\bA^n]$. Since W' is a subset of $W$, $I\subset J$.

Let $J=\I(W')$. Since it is an ideal in Noetherian ring, $J=(f_1, \ldots, f_n)$, $f_i\in I$. I'll write finitely generated ideals shortly in $(f_i)$ if there is no confusion. Let $L=(f_i\circ \varphi)$, then $V'\subset \Z(L)$ since $f_i\circ\varphi(v')=f_i(w')=0$ for all $i$ for some $w'\in W'$ by the definition of $V'$. Conversely let $v\in \Z(L)$, then $f_i\circ\varphi(v)=0$ for all $i$. Since $(f_i)=\I(W')$, $\varphi(v)\in W'$. It implies $v\in \phi^{-1}(W')=V'$. Hence, $V'=\Z\left(\I(W')\right)=W'$ since $W'$ is an affine algebraic subset. The second statement follows interpreting $\tilde{\varphi}:f\mapsto f\circ \varphi$ for $f\in k[W]$ and $\tilde{\varphi}(I)=(f_i\circ \varphi)$ for $I=(f_i)$.
\item[35.] I'll follow the hint given in the problem.

Let $A=\{N'|N'\text{ is a submodule of }M,\text{Ass}_R(N')\subseteq \mathcal{S}\}$. $A$ is partially ordered set with set-theoretic inclusion. Let $C$ be a chain in $A$, then $N=\cup_{N'\in C}N'$ is a submodule of $M$. Since $\Ass(N'')=\cup_{N'\subset C}\Ass(N')$, $N'$ is a submodule of $N''$, $\Ass(N'')\subset \mathcal{S}$. Therefore $N''\in A$ and condition for Zorn's lemma is satisfied. Let $N$ be a maximal submodule of $M$ satisfying $\Ass(N)\subset \mathcal{S}$.

Let $P\in \Ass(M/N)$, then $\exists \overline{m}\in M/N$ such that $R\overline{m}\cong R/P$. $R\overline{m}$ is a submodule of $M/N$ and by lattice isomorphism theorem for module, $\exists M'\subset M$ such that $M'/N\cong R/P$. By problem 31 and 34, $\Ass(M')\subseteq \Ass(N)\cup \Ass(R/P)=\Ass(N)\cup \{P\}$. By the maximality of $N$, $\subsetneq\Ass(M')\subset \Ass(N)\cup \{P\}$. Therefore, $\{P\}\notin \mathcal{S}$ and $P\in \Ass(M)-\mathcal{S}$. It means $\Ass(M/N)\subseteq \Ass(M)-\mathcal{S}$.

Finally, let $\Ass(N)\subsetneq S$. Then $\Ass(M)\subseteq \Ass(M/N)\cup \Ass(N)\subsetneq Ass(M)$ which makes contradiction. Therefore, $\Ass(N)=S$. Also, $\Ass(M)\subseteq \Ass(M/N)\cup \Ass(N)=\mathcal{S}\subset Ass(M)$ with $\Ass(M/N)\subset \Ass(M)-\mathcal{S}$ implies $\Ass(M/N)=\Ass(M)-\mathcal{S}$.
\item[43.] \begin{enumerate}
\item[(a)] Let $G=\{g_1, g_2, \ldots, g_s\}$ be a Gr\"obner basis for the ideal $I$ in $k[x_1, \ldots, x_n]=K[\underline{x}]$ for some monomial ordering. By Buchberger's Criterion, $S(g_i, g_j)\equiv 0 \mod{G}$.(For the definition of $S(f_1, f_2)$, see p. 323 Dummit \& Foote Abstract Algebra.) Since $(g_1, \ldots, g_s)=I$ in $k[\underline{x}]$ and $I'$ is generated by $I$ in $K[\underline{x}]$, $I'\subset (G)$ since $I'=\sum\limits_{t=1}^m R_t i'_t=\sum\limits_{t=1}^m R_t \left(\sum\limits_{j=1}^{l_t} r_j g_j\right)$ where $R_t\in K[\underline{x}]$, $i'_t\in I'$, $r_j\in k[\underline{x}]$, and $g_j\in G$. Therefore, $I'=(G)$ in $K[\underline{x}]$. Furthermore it satisfies Buchberger's Criterion on $K[\underline{x}]$ since it already satisfies the criterion on $k[\underline{x}]$ with respect to the same monomial ordering. Therefore, $G$ is also a Gr\"obner basis for $I'$ in $K[\underline{x}]$ with respect to the same ordering.
\item[(b)] Let $\mathcal{A}$ (resp. $\mathcal{A}'$) be a basis of $k[\underline{x}]/I$. (resp. $K[\underline{x}]/I'$) generated by monomials not divisible by any $LT(g_i)$ according to problem 41. Note that the coefficient of the monomial in $\mathcal{A}$ and $\mathcal{A}'$ does not matter since $k$ and $K$ is a field, so we can set all the monomials in $\mathcal{A}$ and $\mathcal{A}'$ be $1_k=1_K$. Let $f:\mathcal{A}\rightarrow \mathcal{A}'$ such that $f(x^\alpha)=x^\alpha$. ($\alpha$ is multiindex on polynomial.) Then, $f$ is injective because $f(m_1)=f(m_2)$ implies $m_1=m_2$. Also, $f$ is surjective since $m\in \mathcal{A}'$ implies no leading term of $g_i$ in $G$ divides $m$, so $m\in \mathcal{A}$. Hence, the cardinality of $\mathcal{A}'$ equals to $\mathcal{A}$, so the dimension of $k[\underline{x}]/I$ as a vector space over $k$ is equal to the dimension of $K[\underline{x}]/I'$ as a vector space over $K$.
\item[(c)] $I=k[\underline{x}]\Leftrightarrow k[\underline{x}]/I=\{0\}\Leftrightarrow \dim_k k[\underline{x}]/I=0$ for a field $k$ since zero dimension since the dimension of non-trivial vector spaces always have $\dim \geq 1$. Therefore, $I=k[\underline{x}]\Leftrightarrow\dim_k  k[\underline{x}]/I=0\Leftrightarrow\dim_K K[\underline{x}]/I'=0\Leftrightarrow I'=K[\underline{x}]$.
\end{enumerate}
\end{enumerate}

\end{document}